6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-04-09 paper.tex
Additionals and Limitations

\textbf{Scope Limitations:} Due to the significant differences between Windows and UNIX based servers, including compatibility of tools, remote command execution strategies and scriptability, I have decided to target only UNIX based (specifically Linux) servers initially. This decision is based upon the dominance of UNIX within the server market, at 66.8\% in a 2013 study~\cite{UnixMarketShare}.

@@

@@

The application core is a REST API written with the Ruby on Rails framework. It consists of a relational or graph database containing all entities such as hosts, services and their respective dependencies. These entities are exposed via the REST API to other parts of the application. The application core provides the means for registering new hosts and generating appropriate agent configurations.

>>>>

@@

\subsection{Limitations}

Due to the significant differences between Windows and UNIX based servers, including compatibility of tools, remote command execution strategies and scriptability, I have decided to target only UNIX based (specifically Linux) servers initially. This decision is based upon the dominance of UNIX within the server market, at 66.8\% in a 2013 study~\cite{UnixMarketShare}.

The platform limitation will apply to the first version of the tool, but it will be possible to implement a layer of Windows compatibility for verification using a scripting interface such as PowerShell, given extra development time. This enhancement is potentially a good candidate for an open source contribution.

@@

The application core is a REST API written with the Ruby on Rails framework. It consists of a database containing all entities such as hosts, services and their respective dependencies. These entities are exposed via the REST API to other parts of the application. The application core provides the means for registering new hosts and generating appropriate agent configurations.
